\documentclass{report}
\usepackage[utf8]{inputenc}
\usepackage{commath}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{float}
\usepackage{mathtools}
\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
\title{Numerical Simulation-Assignment 2}
\author{Konstantinos Pananas (ANR:658447) }
\date{March 2016}

\begin{document}

\maketitle

\begin{center}
\textbf{\LARGE{Behavioral Economics - Assignment 1}}
\end{center}
\vspace{8mm} 

\textit{Consider the following two-person p-Beauty Contest game. Both players simultaneously choose a number between 0 and 100. Both players have their own target value: p1 and p2, respectively. The player whose number is closest to pi times the average of the two numbers wins a fixed price (e.g., 10 Eurocent). Suppose p1 = 0.7 and p2 = 1.5.}
\bigskip


\begin{itemize}
    \item[] \textit{a) Call the numbers that the players choose x1 and x2, respectively. Write down the inequality that needs to hold for player 1 to win the price}\\

\textbf{Answer:}
$$\abs{x_1 - 0.7 \frac{(x_1 + x_2)}  {2}) } <\abs{  x_2 - 1.5 \frac{(x_1+ x_2 )}{2} }$$
\bigskip

The left hand side of the inequality is the difference between the number that player 1 chooses and p1 times the average of the two numbers. The right hand side of the inequality is the same but for player 2.$\dots$
    \item[]\textit{b) Suppose that player 1 is a level-1 player (who thinks that player 2 is level-0). What number would player 1 choose?}\\

\textbf{Answer:}\\

\begin{align*} 
0.7 \frac{(50 + x_1)}{2} &= x_1 \\ 
\frac{(35 + 0.7x_1)}{2} &= x_1\\
35 + 0.7x_1 &= 2x_1\\
35 &= 1.3x_1\\
x_1 &= \frac{35}{1.3}\\
x_1&\approx26.92\\
\ceil[\big]{x_1}&=27.00
\end{align*}
    \item[]\textit{c) Suppose that player 2 is a level-1 player (who thinks that player 1 is level-0). What number would player 2 choose?}\\

\textbf{Answer:}\\

\begin{align*} 
1.5 \frac{(50 + x_2)}{2} &= x_2\\
\frac{(75 + 1.5x_2)}{2} &= x_2\\
75 + 1.5x_2 &= 2x_2\\
75 &= 0.5x_2\\
x_2 &= \frac{75}{0.5}\\
x_2 &= 150
\end{align*}

However, since the maximum number he can choose, we will choose 100 in all probability.\\
    
    
    \item[]\textit{d) Suppose that player 1 is a level-2 player (who thinks that player 2 is level-1). What number would player 1 choose?}\\

\textbf{Answer:}\\    
    
If player 1 is a level-2 player, he will think that player 2 is level-1 player. This means that he expects that player 2 thinks player 1 is a level-0 player. So he expects player 2 to play 100.\\
    
    \begin{align*} 
0.7 \frac{(100+ x1)}{2} &= x_1\\
\frac{(70 + 0.7x1)}{2} &= x_1\\
70 + 0.7x_1 &= 2x_1\\
70 &= 1.3x_1\\
x_1 &= \frac{70}{1.3}\\
x_1&\approx53.85 \\
\ceil[\big]{x_1}&=54.00
\end{align*}

therefore the player will choose 54\\
    
    
    \item[]\textit{e) Suppose that player 2 is a level-2 player (who thinks that player 1 is level-1). What number would player 2 choose?}\\

\textbf{Answer:}\\

If player 2 is a level-2 player, he will think that player 1 is level-1 player. This means that he expects that player 1 thinks player 2 is a level-0 player. So he expects player 1 to play 27.\\
    
\begin{align*} 
 1.5 \frac{(27 + x_2)}{2} &=x_2\\
  \frac{(40.5 + 1.5x_2)}{2} &= x_2\\
 40.5 + 1.5x_2 &= 2x_2\\
40.5 &= 0.5x_2\\
x_2 &= \frac{40.5}{0.5}\\
x_2&=81 \\
\end{align*}
    \item[]\textit{f) Suppose that player 1 is a level $C_2$ believing that player 2 is a mixture of level-0 and level-1 with $ \tau = 2$. What number would player 1 choose?}\\

\textbf{Answer:}\\

For this question, we will use the Cognitive Hierarchy model. The distribution of levels is assumed to follow a Poisson distribution, meaning that:\\

\begin{align*} 
f(k) &= \frac{e^{-t} t^k}{k!}\\
 Prob (level-k) &=f(k)\\
Prob (level-0) &= \frac{e^{-2}2^0}{0!}\approx0.135\\
Prob(level-1)&= \frac{e^{-2}2^1}{1!}\approx0.271\\
Prob(level-2)&= \frac{e^{-2}2^2}{2!}\approx0.271\\
\end{align*}

\begin{table}[H]
\centering

\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\textbf{Type} & \textbf{Choice} & \textbf{Type} & \textbf{Fraction $f(k)$} & \textbf{Beliefs $C_1$} & \textbf{Beliefs $C_2$} & \textbf{Choice} \\ \hline
$L_0$         & $50$            & $C_0$         & $0,135$                  & $1$                    & $0,33$                 & $50$            \\ \hline
$L_1$         & $100$           & $C_1$         & $0.271$                  & -                      & $0.67$                 & $27$            \\ \hline
$L_2$         & $81$            & $C_2$         & $0.271$                  & -                      & -                      & $45$            \\ \hline

\end{tabular}
\caption{Results Table}


\end{table}



If player 1 is a level C-1 player, he expects that player 2 is a level-0 player. This means that he thinks that player 2 will choose 50 with probability 1. In this case, player 1 will choose 27 (see question (b)).\\

If player 1 is a level C-2 player, he expects that player 2 is a level-0 player with probability 0.33\\
\begin{equation}
 \frac{0.135}{0.135 + 0.271}\approx 0.33
\end{equation}

and a level-1 player with probability 0.67\\
\begin{equation}
\frac{0.271 }{0.135 + 0.271}\approx 0.67
\end{equation}

So he thinks that player 2 will play, from $(1) $ and $(2)$:
$$(0.33 50) + (0.67 100)\approx83.5$$


Therefore player 2 will choose 84.

Therefore player 1 will choose:\\
\begin{align*}
0.7 \frac{(84 + x_1)}{2} &= x_1\\
\frac{(58.8 + 0.7x_1)}{2} &= x_1\\
58.8 + 0.7x_1 &= 2x_1\\
58.8 &= 1.3x_1\\
x_1 &= \frac{58.8}{1.3}\\
x_1&\approx45.23\\
\ceil[\big]{x_1}&=45
\end{align*}

Therefore player 1 will choose 45.\\

    
    
    \item[]\textit{g) Suppose that player 2 is a level C-2 believing that player 1 is a mixture of level-0 and level-1 with $\tau = 2$. What number would player 2 choose?}\\

\textbf{Answer:}\\
\begin{table}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\textbf{Type} & \textbf{Choice} & \textbf{Type} & \textbf{Fraction $f(k)$} & \textbf{Beliefs $C_1$} & \textbf{Beliefs $C_2$} & \textbf{Choice} \\ \hline
$L_0$         & $50$            & $C_0$         & $0,135$                  & $1$                    & $0,33$                 & $50$            \\ \hline
$L_1$         & $27$           & $C_1$         & $0.271$                  & -                      & $0.67$                 & $100$            \\ \hline
$L_2$         & $54$            & $C_2$         & $0.271$                  & -                      & -                      & $100$            \\ \hline

\end{tabular}
\caption{Results Table}


\end{table}

If player 2 is a level C-1 player, he expects that player 1 is a level-0 player. This means that he thinks that player 1 will choose 50 with probability 1. In this case, player 1 will choose 100 (see question (c)).\\


If player 2 is a level C-2 player, he expects that player 1 is a level-0 player with probability 0.33
\begin{equation}
 \frac{0.135}{(0.135 + 0.271)}\approx0.33
\end{equation}

and a level-1 player with probability 0.67\\
\begin{equation}
 \frac{0.271}{0.135+0.271}\approx 0.67
\end{equation}

So he thinks that player 2 will play, from $(3) $ and $(4)$:

$$(0.33 50) + (0.67  27) \approx 34.59$$\\
Roughly, he will choose 35.\\

Therefore player 2 will choose:\\
\begin{align*}
1.5 \frac{(35 + x_2)}{2} &= x_2\\
 \frac{52.5 + 1.5x_2}{2}&= x_2\\
 52.5 + 1.5x_2 &= 2x_2\\
52.5 &= 0.5x_2\\
x_2 &= \frac{52.5}{0.5}\\
x_2&= 105\\
\end{align*}


Therefore player 2 will choose 100 since that is the maximum.\\
\item[]\textit{h) What is the Nash equilibrium for the game?}\\

\textbf{Answer:}\\

Solving the inequality in (a) (it means that $x_1 >.042x_2$), we can say that for every number that player 1 chooses between 1 to 42, player 2 has a best response for it (up to 100). However, since player 2 cannot best respond to numbers higher than 42, if player 1 plays 43, every other number player 2 selects become trivial. So NE will be $b_1>43$ and $b_2=$ any response.Then no player has an incentive to deviate.\\


\end{itemize}








 
     
     


























\end{document}
